---
title: "econometric"
author: "Adam George"
toc: true
eval: false
echo: false
output: false
format: html
page-layout: full
editor: visual
theme: cerulean
code-fold: true
code-tools: true
code-link: true
---

# Preliminary variables

## Dummy variable

```{r}

dummy2009 <- rep(0, L)
dummy2009[86] <- 1

dummycovid <- rep(0, L)
dummycovid[134] <- 1

dummyq1<- rep(c(1,0,0,0), length.out = (L))
dummyq2<- rep(c(0,1,0,0), length.out = (L))
dummyq3<- rep(c(0,0,1,0), length.out = (L))
dummyq4<- rep(c(0,0,0,1), length.out = (L))


dummy <- data.frame(
  dummy2009 = dummy2009[1:(L)],
  dummycovid = dummycovid[1:(L)]
)
```

## Functions

```{r}
setwd(dirname(rstudioapi::getSourceEditorContext()$path)) 
source("estimate.R")
source("econometrics_table.R")


```

# Econometric

## Production

### Labour Productivity

```{r}
#NOT USED

df <- data.frame(
LogPROD = diff((log(lambda[(1):(L)]))) ,
LogGDPR = diff((log(GDP_R[1:L]))),
lKE = diff((log(GCF_R[1:L]-GCF_HHR[1:L])))
)

dummy <- data.frame(
  dummy2009 = dummy2009[1:(L)],
  dummycovid = dummycovid[1:(L)]
)

estimate(df,dummy,50,136)


```

### Wage rate - share per worker

```{r}
df <- data.frame(
WAGESHARE = (W_S[1:L]),
Unemprate = (ru[1:L])
)

dummy <- data.frame(
  dummycovid = dummy2009[1:(L)]
)


result <- estimate(df,dummy,44,136)



econometrics_table(result,end_period = "2022Q4")




result <- glm(df$WAGESHARE ~  df$Unemprate,
    family = quasi(link = "logit", variance = "mu(1-mu)"),data=df)

summary(result)



```

### Wage rate adjustment

```{r}
df <- data.frame(
WAGESHARE = (WR[1:L]),
Unemprate = (W_S[1:L]*(GDP[1:L]/EMP[1:L]))
)

dummy <- data.frame(
  dummycovid = dummycovid[1:(L)]
)


result <- estimate(df,dummy,4,140)



econometrics_table(result,end_period = "2022Q4")



```

### Domestic Prices

```{r}
#NOT CURRENTLY USED

df <- data.frame(
  lp = log(P_P[1:L]),
  lcost = log(UC[1:(L)])
)

dummy <- data.frame(
  dummy2009 = dummy2009[1:(L)]
)



estimate(df,dummy,44,144)



```

### Markups

```{r}
#NOT CURRENTLY USED

df <- data.frame(
  lMU = (MU[1:L]),
  lu = (GDP[1:(L)]/K_P[1:L])
)

dummy <- data.frame(
  dummy2009 = dummy2009[1:(L)]
)



estimate(df,dummy,44,136)


```

### House Prices

```{r}


df <- data.frame(
  LogPriceHouse_POP = log((P_H[1:L]*H[1:L])/POP[1:L]),
  LogYDHH_POP = log(YD_HH[1:(L)]/POP[1:L])#,
  #lIBLHH = log(IBL_HH[1:(L)]/POP[1:L])
)

dummy <- data.frame(
  dummycovid = dummycovid[1:(L)]
)


result <- estimate(df,dummy,88,144)

econometrics_table(result,end_period = "2022Q4")


```

## Rates of Return

### Bank Rate

### NFC Loans

```{r}


df <- data.frame(
  lr = log(r_IBLHH[1:L]-r_BOEQ[1:L]),
  lrbow = log(r_BOEQ[1:L])
)

estimate(df,dummy,5,144)

```

## Households

### Consumption

```{r}

df <- data.frame(
  LogCONSHH = log(c(CONS_HH[1:42]*(CONS_HHP[43]/CONS_HH[43]),CONS_HHP[43:L])),
  LogYDHH = log(YD_HH[1:(L)]),
  LogFNWHH = log(FA_HH[1:(L)])
)

dummy <- data.frame(
  dummy2009 = dummy2009[1:(L)],
  dummycovid = dummycovid[1:(L)]
)

result <- estimate(df,dummy,8,144)

econometrics_table(result,end_period = "2022Q4")

```

### Gross Capital Formation - New Builds

```{r}
df <- data.frame(
  LogGCFHH = log(GCF_HHNB[1:L]),
  LogHVAL = (log(HVAL[1:L]))
)

dummy <- data.frame(
  dummycovid = dummycovid[1:(L)]
)

result <- estimate(df,dummy,88,144)

econometrics_table(result,end_period = "2022Q4")

```

## Non Financial Corporations

### Gross Capital Formation NFC

```{r}


df <- data.frame(
  GCFNFC = ((GCF_NFCD[2:L])/K_NFC[1:(L-1)]),
  Util = (u_NFC_W[2:L])
)
  dummy <- data.frame(
  dummycovid = dummycovid[2:(L)]
) 

result <<- estimate(df,dummy,34,143)

econometrics_table(result,end_period = "2022Q4")

```

### Gross Capital Formation NFC ENERGY

```{r}

df <- data.frame(
  lGCF = GCF_PSFF[1:L],
  elec = (E_ELECFF[1:L]/(K_PSFFR[1:L]*CF_FF))
)

estimate(df,dummy,50,L)
```

### Credit Conditions NFC

```{r}

df <- data.frame(
CR_NFC = (CR_NFC[85:L]) ,
DSR_NFC = (DSR_NFC[84:(L-1)]),
FLMFI_FAMFI = FL_MFI[84:(L-1)]/FA_MFI[84:(L-1)]
)

result <- glm(df$CR_NFC ~  df$DSR_NFC + df$FLMFI_FAMFI,
    family = quasi(link = "logit", variance = "mu(1-mu)"),data=df)

summary(result)

```

### DEF NFC

```{r}
df <- data.frame(
DEF_NFC = DEF_NFC[42:L],
ILLIQ_NFC = ILLIQ_NFC[41:(L-1)]
)

result <- glm(df$DEF_NFC ~  df$ILLIQ_NFC,
    family = quasi(link = "logit", variance = "mu(1-mu)"),data=df)

summary(result)
```

## MFIs

```{r}

```

## NMFIs

### Pension Income

```{r}

df <- data.frame(
  PENSR = (PENSR[1:L]/PENS[1:L]),
  YDNMFI = (YD_NMFI[1:(L)]/PENS[1:L])
)

result <- estimate(df,dummy,50,144)

econometrics_table(result,end_period = "2022Q4")

```

## 

### Pension Income

```{r}
df <- data.frame(
  lINSSR = (INSR[1:L]/INS[1:L]),
  lYD_NMFI = (YD_NMFI[1:(L)]/INS[1:L])
)

result <- estimate(df,dummy,5,144)

econometrics_table(result,end_period = "2022Q4")
```

## Government

```{r}

df <- data.frame(
  SOCBGVT_GDP = (SOCB_GVT[1:L]/GDP[1:L]),
  UnempRate = (ru[1:(L)])
)

result <- estimate(df,dummy,80,144)



econometrics_table(result,end_period = "2022Q4")


```

## RoWs

### Imports

```{r}
df <- data.frame(
LogIMP_FE = log(IMP[1:L]),
LogDY = log(DY[1:L]),
LogGCF = log(GCF[1:L]/DY[1:L]),
LogP_PI = log(P_I[1:L]/P_P[1:L])
)


dummy <- data.frame(
  dummy2009 = dummy2009[1:(L)]
)

result <<- estimate(df,dummy,44,132)


econometrics_table(result,end_period = "2022Q4")
```

### Exports

```{r}
df <- data.frame(
LogEXP_FE = log(EXP[1:L]),
LogRoW_D = log(RoW_D[1:L]*P_F[1:L]),
LogREER = log(P_E[1:L]/(ER[1:L]*P_F[1:L]))
)

dummy <- data.frame(
  dummy2009 = dummy2009[1:(L)]
)

result <<- estimate(df,dummy,44,132)

```
